\bf\mftitle

### 2011-01-21 doc/jInfer/twostep/twostep.tex
3159165 Create documentation fof TwoStep simplifier - better modules images, reflecting cleaners and better layouts
ignores

\section{Using of factory pattern}
TwoStep simplifier is divided into two submodules, which are then divided into submodules and so on.
Each submodule is simply class, properly anotated.
User selects proper classes - submodules in chain to work on inference.
Classes are then, in runtime looked up by using NetBeans lookup mechanism.
But NetBeans holds one instance of each class, that may be looked upon.
When user runs inference first time, classes are looked up and used.
Maybe class members are initialised, instances are in some state after inference completes.
Then, user clicks run button again, and same instances of classes are returned by lookups.
Ooops, theese are not freshly created instances, using them as they are may cause harm.
And problem arises - force each class (submodule) that is being looked up in inference process, to implement
some sort of cleanup method, that would restart it into fresh state and make it ready to use by another 
inference run? Or create new instances of theese classes in each inference run and make singleton classes (those which NetBeans return by lookups) their factory classes?

@@

    // 3. process rules
    final ClusterProcessor<AbstractStructuralNode> processor= clusterProcessorFactory.create();
    for (Cluster<AbstractStructuralNode> cluster : clusterer.getClusters()) {
      final AbstractStructuralNode node =  processor.processCluster(clusterer, cluster.getMembers() - without sentinels);
      // 4. add to rules
      finalGrammar.add(
              new Element(node.getContext(),
              node.getName(),
              node.getMetadata(),
              ((Element) node).getSubnodes(),
              attList);
    }
\end{verbatim}
Task of clustering is dedicated to \jmodule{Clusterer} submodule, and task of infering regular expression for each cluster is dedicated to \jmodule{ClusterProcessor} submodule. We will examine both of them.
Modules currently in jInfer are drawn on fig. \ref{twostep_modules}.
\begin{figure}
	\centering\includegraphics[scale=\myscale]{twostep_modules}
	\caption{Submodules of TwoStep simplifier} \label{twostep_modules}
\end{figure}
We provide one \jmodule{Clusterer} and four \jmodule{ClusterProcessor} implementations.
Each of those will be explained further in this document.

@@

Whole submodule structure of AutomatonMergingState cluster processor is drawn on fig. \ref{automaton_merging_state_submodules}.
\begin{figure}
	\centering\includegraphics[scale=\myscale]{automaton_merging_state_submodules}
	\caption{Submodules of AutomatonMergingState cluster processor} \label{automaton_merging_state_submodules}
\end{figure}
We have implemented \emph{k,h-context} (see \cite{ahonen}) state equivalence in class \code{KHContext}.
We are using state removal method (see \cite{1224321}) to convert regexp automaton into equivalent regular expression.

>>>>

\section{Using of factory pattern}
TwoStep simplifier is divided into three submodules, which are then divided into submodules and so on.
Each submodule is simply class, properly anotated.
User selects proper classes - submodules in chain to work on inference.
Classes are then, in runtime looked up by using NetBeans lookup mechanism.
But NetBeans holds one instance of each class, that may be looked upon.
When user runs inference first time, classes are looked up and used.
Maybe class members are initialised, instances are in some state after inference completes.
Then, user clicks run button again, and same instances of classes are returned by lookups.
Ooops, theese are not freshly created instances, using them as they are may cause harm.
And problem arises - force each class (submodule) that is being looked up in inference process, to implement
some sort of cleanup method, that would restart it into fresh state and make it ready to use by another 
inference run? Or create new instances of theese classes in each inference run and make singleton classes (those which NetBeans return by lookups) their factory classes?

@@

    // 3. process rules
    final ClusterProcessor<AbstractStructuralNode> processor= clusterProcessorFactory.create();
    for (Cluster<AbstractStructuralNode> cluster : clusterer.getClusters()) {
      final AbstractStructuralNode node =  processor.processCluster(clusterer, cluster.getMembers() - without sentinels);
      // 4. add to rules
      finalGrammar.add(
              new Element(node.getContext(),
              node.getName(),
              node.getMetadata(),
              ((Element) node).getSubnodes(),
              attList);
    }
\end{verbatim}
Task of clustering is dedicated to \jmodule{Clusterer} submodule, and task of infering regular expression for each cluster is dedicated to \jmodule{ClusterProcessor} submodule. We will examine both of them.
There is also third submodule called \jmodule{RegularExpressionCleaner} actually, its purpose is just to beatify output regular expressions, no inference logic is implemented there. 
Modules currently in jInfer are drawn on fig. \ref{twostep_modules}.
\begin{figure}
	\centering\includegraphics[scale=\myscale]{twostep_modules}
	\caption{Submodules of TwoStep simplifier} \label{twostep_modules}
\end{figure}
We provide one \jmodule{Clusterer} and four \jmodule{ClusterProcessor} implementations.
Each of those will be explained further in this document.

@@

Whole submodule structure of AutomatonMergingState cluster processor is drawn on fig. \ref{automaton_merging_state_submodules}.
\begin{figure}
	\centering\includegraphics[scale=\myscale]{automaton_merging_state_submodules}
	\caption{Submodules of AutomatonMergingState cluster processor} \label{automaton_merging_state_submodules}
\end{figure}
We have implemented \emph{k,h-context} (see \cite{ahonen}) state equivalence in class \code{KHContext}, which is used by \class{Greedy}
to test mergability of states by default configuration.

\subsubsubsection{StateRemoval}
We are using state removal method (see \cite{1224321}) to convert regexp automaton into equivalent regular expression.
This is implemented in \class{StateRemoval} class.
We defined one submodule of this class with interface called \code{Orderer}.
It has only one method to implement: \code{getStateToRemove}.
Given automaton it has to return reference to one state which should be removed from automaton at first.
State removal calls this submodule and removes states given until there are only two states in automaton - superInitial and superFinal states,
with exactly one transition.
That transition has final regular expression on it as symbol, it is read and returned to AutomatonMergingState.
We implement one orderer, called \code{Weighted}.
It is simple heuristic - weights all states (weight = sum of {in | out | loop}-transition regular expression lengths) and returns state with lowest weight.

\subsection{RegularExpressionCleaner module}
Last we examine \code{RegularExpressionCleaner} interface.
TODO anti cleaners

Whole TwoStep submodules structure is on fig. \ref{twostep_modules_complete}.
\begin{figure}
	\centering\includegraphics[scale=\myscale]{twostep_modules_complete}
	\caption{Modules of TwoStep simplifier and their submodules. Filled classes are default selection (best of).} \label{twostep_modules_complete}
\end{figure}
